### 2014-07-01 tex/main-body-text.tex
clean up merge conflicts

For each set of runs, {\sc flock} reports the 
normalized likelihood values (the exponentiated log-likelihood value for an individual's 
membership to each of $K$ clusters, scaled to sum to one) for a run belonging to the longest plateau (see below).
This value is comparable to the $q_i$ values
returned by {\sc structure}, which, in the no-admixture case, are posterior probabilities of cluster membership.
The program {\sc clumpp} \citep{Jak&Ros2007} was used to relabel clusters among different runs,
while the program {\sc district} \citep{Rosenberg2004} was used to plot individual \textit{$q_i$} values.

@@

\subsection*{Results} 
Run times were relatively short for both programs. All runs of {\sc flock} 
completed in 1133 minutes. Each of the six groups of runs averaged 188.8 minutes.
All runs of {\sc structure} were completed in 
486 minutes and averaged 80.8 minutes to complete each of the six groups of runs. Increasing
$K$ from of 2 to 6 increased the run time for {\sc flock} by a factor of 2.4, while the run time 
for {\sc structure} increased by a factor of only 1.6.

We did not observe major differences among the 
allocation of individuals into K clusters between each program. All six groups 
of {\sc flock} runs for $K = 2$ to $K=4$ yielded nearly identical clustering of individuals 
(See supplementary materials) none of which differed substantially from results obtained with 
{\sc structure} (Fig.~\ref{fig:qplots}). Of the 'best runs' for the six groups for $K=2$, two  
runs yielded identical clustering (same mean LLOD score), all other runs 
differed by at most the allocation of 13 individuals. As 
$K$ increases so does the number of solutions
that {\sc flock} finds (Fig.~\ref{fig:qplots}). For all groups of runs for $K\geq 2$, no plateaus were observed - all initial 
allocations resulted in solutions that differed. These solutions, however, are surprisingly similar to
the cluster membership posterior means identified by {\sc structure}. Both programs identify clusters 
which can be attributed to the geographical boundaries identified by \citet{Garzaetal_norcal}.

Despite the similar allocation of individuals into $K$ clusters, the 
plateau analysis to estimate $K$ in {\sc flock} leads to different conclusions among groups of runs, as well as 
one that differs from {\sc structure}. While no plateaus were observed in any of the six groups 
for a $K\geq 2$, the plateau record varied greatly among each
group for $K = 2$ (plateau sequences: Run1 = 3,2,3,7,4; Run2 = 2,5,2,3,2,3; Run3 = 2,2,2,2,2,5; 
Run4 = 2,3,4,2,4,3; Run5 = 2,2,5,5,3; and; Run6 = 2,2,2,2,2,3,3). The plateau analysis 
procedure suggested by \citet{Duc&Tur2012} leads to 
either an estimate of $K\geq 2$ (Run1) or {\em undecided} as a consequence of no plateau 
lengths being greater than 6. 
\hrule

Interpreting the results from {\sc structure} is often accomplished by 
looking at the estimated log likelihood of the data given K, the delta k method \citep{Evannoetal2005}, and plots of 
individual \textit{$q_i$} values. Both the estimated likelihood of the data
and the plots of individuals \textit{$q_i$} values suggest that 
the most likely \textit{k} for the dataset is 6.

\begin{figure*}
\begin{center}
	 % NOTE. Eric made Flock-Fig1.jpg as a Preview because Flock-Fig1.pdf
	 % ate up too many resources while editing the document.  For final 
	 % production, it should be changed back to Flock-Fig1.pdf
    \includegraphics[width=\textwidth]{images/Figures-Pat/Flock-Fig1-GreyScale.pdf} % Flock-Fig1.jpg}  
    \caption{Assignment to reference population (from \textit{k} = 2-6) plots created 
in the program {\sc flock}. Each horizontal plot represents the 'best run' from a 
series where individuals are reallocated into \textit{k} clusters. Within each plot 
the normalized individual likelihood for each reference population is represented by a 
colored vertical bar. Major geographic boundaries that were attributed to genetic 
structure in \citet{Garzaetal_norcal} are indicated with black vertical lines. Results 
from the 'best runs' showed similar geographic differentiation to 
\citet{Garzaetal_norcal} analysis. The plateau analysis developed by 
\citet{Duc&Tur2012} indicate that either an undecided structure or that \textit{k}=2 
is the lower bound estimate.}
    \label{fig:qplots}
\end{center}
\end{figure*}

\begin{figure*}
\begin{center}
	% NOTE. Pat replaced old Q-val-StrFloc.pdf with a ggplot version 
 \includegraphics[width=25em]{images/Figures-Pat/Fig2.pdf}
    \caption{Individual \textit{$q_i$} values plotted for each cluster for \textit{k}=5. 
{\sc flock} estimates of likelihood of assignment to each cluster have less uncertainty
 attributed to them.}
    \label{fig:qscatter}
\end{center}
\end{figure*}

>>>>

For each set of runs, {\sc flock} reports the 
normalized likelihood values (the exponentiated log-likelihood value for an individual's 
membership to each of $K$ clusters, scaled to sum to one) for a run belonging to the longest plateau - refered to as the 'best run' by \citep{Duc&Tur2012} (see below).
This value is comparable to the $q_i$ values
returned by {\sc structure}, which, in the no-admixture case, are posterior probabilities of cluster membership.
The program {\sc clumpp} \citep{Jak&Ros2007} was used to relabel clusters among different runs,
while the program {\sc district} \citep{Rosenberg2004} was used to plot individual \textit{$q_i$} values.

@@

\subsection*{Results} 
Run times for both programs were relatively short, albeit non-trivial. All runs of {\sc flock} 
completed in 1133 minutes. Each of the six groups of runs averaged 188.8 minutes.
All runs of {\sc structure} were completed in 
486 minutes and averaged 80.8 minutes to complete each of the six groups of runs.
The processing time of each algorithm increased with as the number or 
putative clusters increases. Increasing
$K$ from of 2 to 6 increased the run time for {\sc flock} by a factor of 2.4, while the run time 
for {\sc structure} increased by a factor of only 1.6.

{\sc flock} and {\sc structure} provide similar results in 
terms of how individuals are allocated among runs at low values of $K$, 
while, at larger values, {\sc flock} often found, in addition to the solution identified by {\sc structure}, 
multiple other solutions. For all six groups 
of runs for \textit{k} = 2 - 4, {\sc flock} resulted in nearly identical clustering of individuals 
(See supplementary materials) none of which differed substantially from results obtain from 
{\sc structure} (Fig 1). Of the 'best runs' for the six groups for \textit{k} of 2, two  
runs yielded identical clustering (same mean LLOD score), all other runs 
differed by at most the allocation of 13 individuals. As 
\textit{k} increases so do the number of solutions
that {\sc flock} finds (Fig 1). For all groups of runs for $K$ $\geq 2$, no plateaus were observed - all intial 
allocations resulted in solutions that differed. 
It is unclear in these cases what constitutes the 'best run' as all plateau lengths are 
equal to one. Many of these solutions are, however, suprisingly similar to
 the partions identified by {\sc structure}. Both programs idenfity clusters 
which can be attributed to the geographical boundaries identified by \citet{Garzaetal_norcal},
although less reliably so in the case of {\sc flock}.

Despite the similar allocation of individuals into $K$ clusters, the 
plateau analysis to estimate $K$ in {\sc flock} leads to different conclusions among groups of runs, as well as 
one that differs from {\sc structure}. While no plateaus were observed in any of the six groups 
for a $K\geq 2$, the plateau record varied greatly among each
group for $K = 2$ (plateau sequences: Run1 = 3,2,3,7,4; Run2 = 2,5,2,3,2,3; Run3 = 2,2,2,2,2,5; 
Run4 = 2,3,4,2,4,3; Run5 = 2,2,5,5,3; and; Run6 = 2,2,2,2,2,3,3). The plateau analysis 
procedure suggested by \citet{Duc&Tur2012} leads to
either an estimate of K $\geq$ 2 (Run1) or {\em undecided} as a consequence of no plateau 
lengths being greater than 6. The ($\ln P(D)$) from {\sc structure}
was largest at $K$ = 6 which was supported by the $q_i$ plots. The $\Delta K$ method, however, 
supports a $K$ = 2.

\hrule

\begin{figure*}
\begin{center}
	 % NOTE. Eric made Flock-Fig1.jpg as a Preview because Flock-Fig1.pdf
	 % ate up too many resources while editing the document.  For final 
	 % production, it should be changed back to Flock-Fig1.pdf
    \includegraphics[width=\textwidth]{images/Figures-Pat/Flock-Fig1-GreyScale.pdf} % Flock-Fig1.jpg}  
    \caption{Plots of $q_i$ values from {\sc structure} and the normalized likelihood values 
from {\sc flock} made in the program Distruct. Each horizontal plot represents an individual run of the program {\sc structure}, or the 'best run' from a series of runs in {\sc flock}. Within each plot 
$q_i$ values from {\sc structure} and the normalized likelihood values 
from {\sc flock}  are represented by a 
colored vertical bar.  Results from 
from the 'best runs' of {\sc flock} showed similar geographic differentiation to 
\citet{Garzaetal_norcal}.}
    \label{Fig.1}
\end{center}
\end{figure*}

\begin{figure}
\begin{center}
	% NOTE. Pat replaced old Q-val-StrFloc.pdf with a ggplot version 
 \includegraphics[width=25em]{images/Figures-Pat/Fig2.pdf}
    \caption{Individual \textit{$q_i$} values plotted for each cluster for \textit{k}=5. 
{\sc flock} estimates of likelihood of assignment to each cluster have less uncertainty
 attributed to them.}
    \label{fig:qscatter}
\end{center}
\end{figure}
